Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-15 paper_knowledge.tex
Added bibliography
Integrated Raquel changes on abstract/introduction

\begin{abstract}
This paper presents how extraction, representation and use of symbolic
knowledge from real-world perception and human-robot verbal and non-verbal
interaction can actually enable a grounded and shared model of the world that
is suitable for later high-level tasks like dialogue understanding. We show how
the anchoring process itself relies on the situated nature of human-robot
interactions. We present an implementation, including a specialized symbolic
knowledge representation approach based on Description Logics, and experiments
on several robotic platforms that demonstrate these cognitive capabilities.
\end{abstract}

@@

A messy table, covered with cardboard boxes, books, video tapes... Thomas is
moving and packs everything with the help of Jido, its robot
(Fig.~\ref{fig|vpt}).

`` -- Jido, give me this'', says Thomas, looking at a box that contains a video
tape. The robot smoothly grasps the tape, and hands it to the human.

@@

To be combined together, those abilities require an unambiguous and shared
representation of concepts (objects, agents, actions...) underlying the
interaction: what are the prerequisites for such a
human sentence --- ``Jido, give me this'' --- to be understood by the robot,
correctly interpreted in the spatial context of the interaction, and ultimately
transformed into an action?

Austin~\cite{Austin1962} would have at first glance analyzed such kind of
sentence as a \emph{speech act}, comprising of \emph{locutionary},
\emph{illocutionary} and possibly \emph{perlocutionary} acts. First, we want to
understand the direct meaning of the sentence (\emph{locutionary act}): we must
acquire the sentence, convert it into a useful syntactic form (quite probably
by mean of speech recognition), and understand the semantics of the sentence,
\ie, What is refered by ``\textit{Jido}''? What is ``\textit{give}''? What is
``\textit{me}''? And ``\textit{this}''?

Working in a situated context, we want furthermore to \emph{resolve} these
semantics atoms, \ie ground them in the sensory-motor space of the robot. For
instance, ``\textit{this}'' is a demonstrative pronoun that refers in this
context to the object the human is focusing on, whatever \textit{focusing}
means: here, Thomas is looking at something, which is a possible cue. But it
could as well point at something or refer to some previously mentioned concept.

@@

Second, the \emph{illocutionary force}, \ie the \emph{intent} of the utterance
as thought by the agent must be extracted, and understood. In our example,
Thomas obviously wants an action to be performed by the robot. The action
parametrization is conveyed by the semantics attached to the words and the
grammatical structures of the sentence. In our example, the type of action is
given by the verb ``\textit{give}''. Assuming the robot has some procedural
knowledge attached to this symbol, the action type can be considered as
grounded for the robot. We can as well understand that the recipient of the
action is the human, the performer is the robot itself, and the object acted
upon is the tape. These are the basic \emph{thematic roles}~\cite{Gruber1965}
that can be extracted from the sentence that allow to fully ground the action.

Ultimately, an implicit speaker's expectation can sometimes be conveyed --- the
\emph{perlocutionary act} --- that must be taken into account. If Thomas would
have said instead `` -- Jido, this box is too heavy for me'', he implicitly
expects the robot to memorize the fact that the box's weight is over his
capabilities, and it may as well imply that Thomas is requiring help to carry
the box.

@@

Extracting these speech acts and turning them into a content processable by the
robot is a difficult challenge in the general case. We base our approach on
three distinct, inter-related cognitive functions.
Figure~\ref{fig|overall-process} illustrates the general context, while
Figure~\ref{fig|main-components} summarizes the interactions between the three
main components.

@@

\item \emph{Physical environment modeling} and \emph{spatial reasoning}
(grouped under the term \emph{situation assessment})  are in charge of building
and maintaining a coherent model of the physical world. This model is realistic
in the sense that it relies on accurate 3D models of both manipulated objects
and humans. It also has dedicated mechanisms to manage disappearing or occluded
objects.  The geometric model is used to compute several spatial properties of
the scene that actually convert the original sensory data into symbolic
beliefs. This includes relative locations of objects, visibility state,
gestures like pointing, etc.  Assuming that other agents are as well
represented in the model, the same computations are applied to analyze the
scene from each agents' point of view (\ie from their \emph{perspectives}).

\item \emph{Knowledge representation and management}: the robot is endowed with
an active knowledge base that provides a logically sound symbolic model of its
beliefs on the world, as well as models for each cognitive agent the robot
interacts with. Each of these models is independent and logically consistent.
This enable reasoning on different perspectives of the world that would be
considered otherwise inconsistent (for instance, an object can be visible for
the robot but not for the human. This object can have at the same time the
property \concept{isVisible \textbf{true}} and \concept{isVisible \textbf{false}}, in
two different models).  Our platform also features continuous storage, querying
and event triggering over the pool of facts known by the robot. It relies on
OWL ontologies (a decidable subset of the predicate logics).

Used in combination with the situation assessment framework, the robot is thus
able to maintain different symbolic models of the world, one per agent. This proves an
essential feature (\cite{Roy2005,Kruijff2010}) to enable perspective-aware
grounding of natural language, as we will see in next sections.

\item \emph{Dialogue input processing}, including natural language parsing
capabilities, disambiguation routines and interactive concept anchoring. We
focused our efforts on three classes of utterance, commonly found in
human-robot interaction: \emph{statements} (\ie new facts the human wants to
inform the robot), \emph{orders} (or more generically \emph{desires}) and
\emph{questions on declarative knowledge} (whose answers do not require
explicit planning). This would roughly cover the \emph{representative}
(sometimes referred as \emph{assertives}) and \emph{directives} type of
illocutionary acts, in Searle~\cite{Searle1976} classification.

@@

Based on these three components, we have developed several grounding mechanisms
for situated verbal interaction, integrated into a broader control architecture
for indoors service robots.

@@

Processing natural language in situated context is already an established
research field. In~\cite{Roy2005}, Roy and Reiter summarize what they see as the main
challenges to be tackled: cross-modal representation systems, association of
words with perceptual and action categories, modeling of context, figuring out
the right granularity of models, integrating temporal modeling and planning,
the ability to match past (learned) experiences with the current interaction
and the ability to take into account the human perspective. This list offers an
interesting entry point to evaluate our contribution.

Kruijff et al. provides in~\cite{Kruijff2010} an up-to-date survey of literature
on situated human-robot dialogue, focusing on formal representation systems,
bi-directionality of the interaction and context building. They point out as well
that, compared to the cognitive psychology community, the ``situated AI''
community started only recently to take into account agents focus, perspective and temporal
projection abilities.

Dialogue processing on real robots have been explored by several teams.
Brick and Scheutz~\cite{Brick2007} have contributions regarding natural language
processing in an incremental way, and how this enables instant back-channel
feedback (like nodding).

Hüwel et al.~\cite{Huwel2006} propose the concept of \textit{Situated Semantic
Unit}: these meaning atoms are extracted from sentences and expose semantic
links to other units. The parser tries to satisfy these links and rate
accordingly the semantic interpretation of the sentence. Used in conjunction
with ontologies, their approach offers good robustness to ungrammatical or
partial utterances. They validated the approach with an extensive user-study.

While mostly implemented on virtual agents, the GLAIR cognitive architecture
by Shapiro and Bona~\cite{Shapiro2009} is an architecture
explicitly built to tackle the grounding issue from the percept to the
decision. It is a three-layers architecture: a \emph{Knowledge Layer}, a
low-level \emph{Sensori-Actuator Layer} and an intermediate
\emph{Perceptuo-Motor Layer} that binds the previous two.  The knowledge layer
relies on a custom knowledge representation language (more expressive than
first-order logic), and natural language processing capabilities similar to
ours are available. The GLAIR project has been only demonstrated in a limited
set of environments, but exhibits interesting features like explicit management
of contexts of facts and memory models (long term/short term,
episodic/semantic).

Also worth mentioning, Mavridis and Roy~\cite{Mavridis2005} propose the idea of
a \emph{grounded situation model} which is an amodal model of the world where
different sensing modalities, including verbal ones (the robot is able to
\emph{imagine} objects), are merged. Their framework also allows management of
the interaction history (the human can ask for a past event). They propose an
implementation in an environment built on simple entities (a manipulator arm
and color balls).

@@

Suh et al.~\cite{Suh2007} develop {\sc OMRKF}, an ontology-based reasoning
framework for robotics. They try to tackle the grounding issue by storing low-level facts
(like SIFT visual features) in a layered symbolic architecture that works well
in simple sensori-motor spaces. However this approach raises concerns regarding
scalability and management of more complex entities or interactions.

Daoutis et al.~\cite{Daoutis2009} introduce one of the first complete
architecture for grounded human-robot interaction. They successfully bind
low-level percepts (including view-point independent SIFT based object
recognition) to a high-level knowledge representation and reasoning system via
a dedicated anchoring module. They base their knowledge
model directly on the \textit{ResearchCyc} ontology (including the
\textit{MicroTheories} concept), used in combination with the \textsc{CycL}
language. This enables second-order logic modeling and access to a large
common-sense knowledge base.

Beetz et al.~\cite{Beetz2010} proposes a cognitive architecture called \textsc{CRAM}
(Cognitive Robot Abstract Machine) that integrates
\textsc{KnowRob}~\cite{Tenorth2009a}, a knowledge processing framework based on
Prolog. Its underlying storage is based on an RDF/OWL\footnote{RDF/OWL is a
standard for Description Logics based ontology
(\url{http://www.w3.org/TR/owl2-primer/}).} ontology, derived from
\textsc{OpenCyc}. \textsc{CRAM} and \textsc{KownRob} have been demonstrated on
several real-world scenarios, where natural language recipes extracted from
Internet had to be translated into plans and executed in a kitchen environment,
perceived and rebuilt on-line by the robots. While Prolog offers more flexible
modeling (no constraints on the arity of predicate, where Description Logics as
used in our work is limited to binary predicates), it is based on the closed
world assumption (if something cannot inferred to be true, it is inferred to be
false) whereas we rely on the open world assumption, which is more realistic in
real world scenarii. A probabilistic extension of \textsc{KnowRob}, called
\textsc{ProbCog}~\cite{Jain2009} is available. While in principle possible, the
CRAM architecture does not provide currently explicit support for the
interaction with humans.

\subsection{Contribution}

Besides proposing a new integration model for sensor data, natural language and
symbolic knowledge repositories, our work extends these previous
contributions by tackling more realistic human-robot interactions: open
speech; complex, dynamic, partially unknown human environments; fully
embodied (with arms, head, ability to move,...) autonomous robots that can
perform manipulation.

Four specific contributions are presented in this work: first, we introduce in
this paper a novel and versatile knowledge base that models in a
formal framework, based on first-order logics, not only the robot's own beliefs
but also every other cognitive agent the robot interacts with.  This explicit
modeling of other agents' belief states is used for the interaction and eases
the implementation of various advanced cognitive behaviours like learning
new concepts or interactive objects discrimination.

Second, we have implemented a framework to extract symbolic facts from complex
real scenes. It is based on a 3D model of the world that the robot builds
on-line by merging sensor modalities. It computes in real-time spatial
relations between perceived objects and it allows to virtually \emph{view} the
same scene from different point of view, enabling \emph{visual} and
\emph{spatial agent perspective taking}.

@@

Lastly, our architecture moves away from standard layered approaches. The way
our different components interact together is not easily represented as a
layered architecture because components interactions are mostly bidirectional.
This is especially visible for the dialogue input processing: this component
does not simply act as an alternative perceptual input to the symbolic
database, but also actively queries previously acquired knowledge to
disambiguate and validate the newly created symbolic knowledge. This behaviour
leads us to the idea of \emph{knowledge-oriented architecture} which is
detailed later on.

@@

In the next section, we present in depth the so-called {\sc ORO}
(\emph{OpenRobots Ontology} server) knowledge base, a dynamic knowledge
representation system based on Description Logics ontologies and relying on the
\emph{Open World Assumption}. We present it first, along with its objectives,
since it is the knowledge \textit{hub} of the system, used pervasively by other
components.

Section 3 presents the {\sc SPARK} (for \emph{SPAtial Reasoning \& Knowledge})
module that merges perceptual information with a coherent geometric model and
builds a symbolic interpretation of the world from the robot point of view. It
also computes an individual symbolic model for each agent currently present in
the environment.

Section 4 covers in details the dialogue processing component. The main
algorithms for natural language grounding are detailed. Interactions between
this component and the knowledge base are described.

Section 5 presents three experiments that were conducted on three different
robotic platforms: the \emph{naming} experiment, where a robot anchors new
knowledge in its model through verbal interaction; the \emph{Spy Game} where
either the user or the robot tries to guess which object the other player is
thinking of; and a more complex experiment situated in an everyday setup where
the robot builds models for several agents and interacts with the users using
this knowledge.

@@

\bibliographystyle{spbasic}
%\bibliography{/home/slemaign/work/biblio/biblio_phd_severin}
\bibliography{/media/Documents/These/work/biblio/biblio_phd_severin}

>>>>

\begin{abstract}
This paper presents how extraction, representation and use of symbolic
knowledge from real-world perception and human-robot verbal and non-verbal
interaction can actually enable a grounded and shared model of the world that
is suitable for later high-level tasks such as dialogue understanding. We show how
the anchoring process itself relies on the situated nature of human-robot
interactions. We present an implementation, including a specialized symbolic
knowledge representation approach based on Description Logics, and case studies
on several robotic platforms that demonstrate these cognitive capabilities.
\end{abstract}

@@

A messy table, covered with cardboard boxes, books, video tapes... Thomas is
moving out and is packing everything with the help of Jido, his robot
(Fig.~\ref{fig|vpt}).

``Jido, give me this'', says Thomas while looking at a box that contains a
video tape. The robot smoothly grasps the tape, and hands it to the him.

@@

To be combined together, those abilities require an unambiguous and shared
representation of concepts (objects, agents, actions...) underlying the
interaction: what are the prerequisites for such a human sentence --``Jido,
give me this''-- to be understood by the robot, correctly interpreted in the
spatial context of the interaction, and eventually transformed into an action?

Austin~\cite{Austin1962} would have at first glance analyzed such kind of
sentence as a \emph{speech act}, comprising of \emph{locutionary},
\emph{illocutionary} and possibly \emph{perlocutionary} acts. First, we want to
understand the direct meaning of the sentence (\emph{locutionary act}): we must
acquire the sentence, convert it into a useful syntactic form (probably through
speech recognition), and understand the semantics of the sentence, \ie What is
referred by ``\textit{Jido}''? What is ``\textit{give}''? What is
``\textit{me}''? And ``\textit{this}''?

Working in a situated context, we want furthermore to \emph{resolve} these
semantics atoms, \ie ground them in the sensory-motor space of the robot. For
instance, ``\textit{this}'' is a demonstrative pronoun that refers in this
context to the object the human is focusing on (whatever \textit{focusing}
means). In this example Thomas is looking at something, which is a possible
cue. But it could as well be pointing at something or making reference to some
previously mentioned concept.

@@

Second, the \emph{illocutionary force}, \ie the \emph{intent} of the utterance
as thought by the agent, must be extracted and understood. In our example,
Thomas obviously wants an action to be performed by the robot. The action
parametrization is conveyed by the semantics attached to the words and the
grammatical structures of the sentence. In our example, the type of action is
given by the verb ``\textit{give}''. Assuming the robot has some procedural
knowledge attached to this symbol, the action type can be considered as
grounded for the robot. We can as well understand that the recipient of the
action is the human, the performer is the robot itself, and the object acted
upon is the tape. These are the basic \emph{thematic roles}~\cite{Gruber1965}
that can be extracted from the sentence that allow to fully ground the action.

Finally, the implicit speaker's expectation can sometimes be conveyed --the
\emph{perlocutionary act}-- and should be taken into account. If Thomas would
have said instead ``Jido, this box is too heavy for me'', he may implicitly
expect the robot to memorize the fact that the box's weight is over his
capabilities, and it may as well imply that Thomas is requiring help to carry
the box.

@@

Extracting these speech acts and turning them into a content processable by the
robot is a difficult challenge in the general case. We base our approach on
three distinct, inter-related cognitive functions.
Figure~\ref{fig|overall-process} illustrates the general context, while
Figure~\ref{fig|main-components} summarizes the interactions between the three
main components:

@@

\item \emph{Physical environment modeling} and \emph{spatial reasoning}
(grouped under the term \emph{situation assessment}): these components are in
charge of building and maintaining a coherent model of the physical world. This
model is realistic in the sense that it relies on accurate 3D models of both
manipulated objects and humans. It also has dedicated mechanisms to manage
disappearing or occluded objects.  The geometric model is used to compute
several spatial properties of the scene that actually convert the original
sensory data into symbolic beliefs, including relative locations of objects,
visibility state, gestures (such as pointing), etc.  Assuming that other agents
are also represented in the model, the same computations are applied to analyze
the scene from each agent's point of view (\ie from their \emph{perspectives}).

\item \emph{Knowledge representation and management}: the robot is endowed with
an active knowledge base that provides a logically sound symbolic model of its
beliefs of the world, as well as models for each cognitive agent the robot
interacts with. Each of these models is independent and logically consistent,
enabling reasoning on different perspectives of the world that would otherwise
be considered inconsistent (for instance, an object can be visible for the
robot but not for the human. This object can have at the same time the property
\concept{isVisible \textbf{true}} and \concept{isVisible \textbf{false}} using
two different models).  Our platform relies on OWL ontologies (a decidable
subset of the predicate logics) featuring continuous storage, querying and
event triggering over the pool of facts known by the robot.

Used in combination with the situation assessment framework, the robot is thus
able to maintain different symbolic models of the world, one per agent. This
proves an essential feature (\cite{Roy2005,Kruijff2010}) to enable
perspective-aware grounding of natural language as we will see in next
sections.

\item \emph{Dialogue input processing}: a subsystem which includes natural
language parsing capabilities, disambiguation routines and interactive concept
anchoring. We focused our efforts on three classes of utterances commonly found
in human-robot interaction: \emph{statements} (\ie new facts the human wants to
inform the robot), \emph{orders} (or more generically \emph{desires}) and
\emph{questions on declarative knowledge} (whose answers do not require
explicit planning). This would roughly cover the \emph{representative}
(sometimes referred as \emph{assertive}) and \emph{directive} illocutionary
acts in Searle~\cite{Searle1976} classification.

@@

Based on these three components we have developed several grounding mechanisms
for situated verbal interaction and integrated them into a broader control
architecture for indoors service robots.

@@

Processing natural language in situated context is already an established
research field. In~\cite{Roy2005}, Roy and Reiter summarize what they see as
the main challenges to be tackled: cross-modal representation systems,
association of words with perceptual and action categories, modeling of
context, figuring out the right granularity of models, integrating temporal
modeling and planning, ability to match past (learned) experiences with the
current interaction and ability to take into account the human perspective.
This list offers an interesting entry point to evaluate our contribution.

Kruijff et al. provides in~\cite{Kruijff2010} an up-to-date survey of
literature on situated human-robot dialogue, focusing on formal representation
systems, bi-directionality of the interaction and context building. They point
out as well that compared to the cognitive psychology community, the ``situated
AI'' community started only recently to take into account agents' focus of
attention, perspective and temporal projection abilities.

Dialogue processing in real robots have been explored by several teams.  Brick
and Scheutz~\cite{Brick2007} have contributions regarding natural language
processing in an incremental way, and how this enables instant back-channel
feedback (like nodding). Hüwel et al.~\cite{Huwel2006} propose the concept of
\textit{Situated Semantic Unit}: atoms are extracted from sentences exposing
semantic links to other units. The parser tries to satisfy these links and
rates the semantic interpretation of the sentence. Used in conjunction with
ontologies, their approach offers robustness to ungrammatical or partial
utterances. They validated the approach with an extensive user-study.

While mostly implemented on virtual agents, the GLAIR cognitive architecture by
Shapiro and Bona~\cite{Shapiro2009} is an architecture explicitly built to
tackle the grounding issue from the percept to the decision. It is a
three-layers architecture: a \emph{Knowledge Layer}, a low-level
\emph{Sensori-Actuator Layer} and an intermediate \emph{Perceptuo-Motor Layer}
that binds the previous two.  The knowledge layer relies on a custom knowledge
representation language (more expressive than first-order logic), and natural
language processing capabilities similar to ours are available. The GLAIR
project has been only demonstrated in a limited set of environments, but
exhibits interesting features such as explicit management of contexts of facts
and memory models (long term/short term, episodic/semantic).

Also worth mentioning, Mavridis and Roy~\cite{Mavridis2005} propose the idea of
a \emph{grounded situation model} which is an a-modal model of the world where
different sensing modalities, including verbal ones (the robot is able to
\emph{imagine} objects), are merged. Their framework also allows management of
the interaction history (the human can ask for a past event). They propose an
implementation in an environment built on simple entities (a manipulator arm
and color balls).

@@

Suh et al.~\cite{Suh2007} develop {\sc OMRKF}, an ontology-based reasoning
framework for robotics. They tackle the grounding problem by storing low-level
facts (like SIFT visual features) in a layered symbolic architecture that works
well in simple sensori-motor spaces. However this approach raises concerns
regarding scalability and management of more complex entities or interactions.

Daoutis et al.~\cite{Daoutis2009} introduce one of the first complete
architectures for grounded human-robot interaction. They successfully bind
low-level percepts (including view-point independent SIFT based object
recognition) to a high-level knowledge representation and reasoning system via
a dedicated anchoring module. They base their knowledge model directly on the
\textit{ResearchCyc} ontology (including the \textit{MicroTheories} concept),
used in combination with the \textsc{CycL} language. This enables second-order
logic modeling and access to a large common-sense knowledge base.

Beetz et al.~\cite{Beetz2010} proposes a cognitive architecture called
\textsc{CRAM} (Cognitive Robot Abstract Machine) that integrates
\textsc{KnowRob}~\cite{Tenorth2009a}, a knowledge processing framework based on
Prolog. Its underlying storage is based on an RDF/OWL\footnote{RDF/OWL is a
standard for Description Logics based ontology
(\url{http://www.w3.org/TR/owl2-primer/}).} ontology, derived from
\textsc{OpenCyc}. \textsc{CRAM} and \textsc{KownRob} have been demonstrated on
several real-world scenarios, where natural language recipes extracted from
Internet had to be translated into plans and executed in a kitchen environment,
perceived and rebuilt on-line by the robots. While Prolog offers more flexible
modeling (no constraints on the arity of predicate, where Description Logics as
used in our work are limited to binary predicates), it is based on the closed
world assumption (if something cannot be inferred to be true, it is inferred to
be false) whereas we rely on the open world assumption, which is more realistic
in real world scenarios. A probabilistic extension of \textsc{KnowRob}, called
\textsc{ProbCog}~\cite{Jain2009} is also available. While in principle
possible, currently the CRAM architecture does not provide explicit support for
interacting with humans.

\subsection{Contributions}

Besides proposing a new integration model for sensor data, natural language and
symbolic knowledge repositories, our work extends these previous contributions
by tackling more realistic human-robot interactions: open speech; complex,
dynamic, partially unknown human environments; and fully embodied (with arms,
head, ability to move,...) autonomous robots that can perform manipulation.

Four specific contributions are presented in this work: first, we introduce a
novel and versatile knowledge base that models in a formal framework, based on
first-order logics, not only the robot's own beliefs but also every other
cognitive agent the robot interacts with.  This explicit modeling of other
agents' belief states is used for the interaction and eases the implementation
of various advanced cognitive behaviours like learning new concepts or
interactive objects discrimination.

Second, we have implemented a framework to extract symbolic facts from complex
real scenes. It is based on a 3D model of the world that the robot builds
on-line by merging different sensor modalities. It computes spatial relations
between perceived objects in real-time and it allows to virtually \emph{view}
the same scene from different points of view, enabling \emph{visual} and
\emph{spatial agent perspective taking}.

@@

Lastly, our architecture moves away from standard layered approaches. The way
our different components interact together is not easily represented as a
layered architecture because interactions among components are mostly
bidirectional.  This is especially visible for the dialogue input processing:
this component does not simply act as an alternative perceptual input to the
symbolic database, but also actively queries previously acquired knowledge to
disambiguate and validate the newly created symbolic knowledge. This behaviour
leads us to the idea of \emph{knowledge-oriented architecture}, which is
detailed later on.

@@

In the next section we present in depth the so-called {\sc ORO}
(\emph{OpenRobots Ontology} server) knowledge base, a dynamic knowledge
representation system based on Description Logics ontologies and relying on the
\emph{Open World Assumption}. We present it first, along with its objectives,
since it is the knowledge \textit{hub} of the system, used pervasively by other
components.

Section 3 presents {\sc SPARK} (for \emph{SPAtial Reasoning \& Knowledge}), a
module that merges perceptual information with a coherent geometric model and
builds a symbolic interpretation of the world from the robot's point of view,
as well as an individual symbolic model for each agent currently present in the
environment.

Section 4 covers in detail the dialogue processing component. The main
algorithms for natural language grounding are described, as well as the
interactions between these component and the knowledge base.

Section 5 presents three use-cases that were conducted on three different
robotic platforms: the \emph{naming} experiment, where a robot anchors new
knowledge in its model through verbal interaction; the \emph{Spy Game} where
either the user or the robot tries to guess which object the other player is
thinking of; and a more complex experiment situated in an everyday setup, where
the robot builds models for several agents and interacts with the users using
this knowledge.

@@

\bibliographystyle{spbasic}
\bibliography{biblio}
